### 2018-10-21 coverletter/coverletter.tex
Version 3.1

This paper is extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
This paper makes the following distinct contributions compared with the conference paper.

\begin{enumerate}
\item 
We propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model displays utilization of resources in the time dimension and calculates execution time of computing jobs on different DAG frameworks. We use the FRQ model to assist in analyzing the shuffle process and verify SCache shuffle optimization by mathematics.  
% Furthermore, the FRQ model can calculate the execution time of DAG framework under difference resources allocation strategies. 
\item 
In the conference paper, we only implemented SCache on Spark. To prove the compatibility of SCache as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
Our experiments show that SCache can also optimize the computing performance of Hadoop MapReduce.
\item
We append two parts in the evaluation section. Firstly, we verify the FRQ model in both our in-house environment and Amazon EC2 environment. The error between the calculated value and the experimental value is basically below $10\%$. Secondly, we evaluate the performance of Hadoop MapReduce with SCache in the same environment as the conference paper.
After utilizing pre-fetching of SCache, Hadoop MapReduce with SCache optimize job completion time by up to $15\%$ and an average of $13\%$.
\end{enumerate}

Besides the major contributions, we also revise the paper in many places, including writing and more related work. We believe that the added content makes sufficient contribution to this journal submission.

>>>>

This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
This paper makes the following distinct contributions compared with the conference paper.

\begin{enumerate}
\item 
We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
The proposed model is not only to predict the job completion time, but also to theoretically analyze DAG frameworks.
The FRQ models DAG frameworks according to the resource scheduling strategy of each DAG framework by mutiple parameters.
Through modeling, the FRQ model can indicate which parameters of the DAG framework are important and which parts of the DAG framework can be optimized. 
Furthermore, the FRQ models can classify DAG frameworks based on their scheduling stratagies.
According to the theoretical analysis results of the FRQ model, we are able to optimize DAG frameworks more accurately.
% We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ models utilization of resources in the time dimension and calculates the execution time of computing jobs on different DAG frameworks. 
% We use this FRQ model to assist in analyzing the shuffle process. 
% The FRQ model can evaluate the scheduling strategies of DAG computing frameworks, such as Hadoop MapReduce and Spark, and help us optimize them. 
% The FRQ model provides a theoretical basis for performance optimization of SCache.
% We use the FRQ model to assist in analyzing the shuffle process and verify SCache shuffle optimization by mathematics.  
% Furthermore, the FRQ model can calculate the execution time of DAG framework under difference resources allocation strategies. 
\item 
In the conference paper, we only implemented SCache on Spark. To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
Our experiments show that SCache can also optimize the computing performance of Hadoop MapReduce.
\item
We append two parts to the evaluation section. Firstly, we evaluate the FRQ model in both our in-house environment and Amazon EC2 environment. The error between the FRQ’s calculated value and the experimental value is below $10\%$. Secondly, we evaluate the performance of Hadoop MapReduce with SCache. A in the same environment as the conference paper, i.e., 50-node Amazon EC2 cluster.
After utilizing pre-fetching of SCache, Hadoop MapReduce with SCache optimize job completion time by up to $15\%$ and an average of $13\%$.
\end{enumerate}

% Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
In summary, we propose a new performance model to provide theoretical basis for performance optimization and improve experiments by adding experiments on Hadoop MapReduce. 
We believe that the added content makes a sufficient contribution to this journal submission.

### 2018-10-21 tex/conclusion.tex
Version 3.1

\section{Conclusion}
In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By tasks pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{black}
Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. At last we use the FRQ model to verify SCache shuffle optimization by mathematics.
Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 
}

>>>>

\section{Conclusion}
In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By task pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{black}
Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. At last we evaluate the SCache shuffle optimization by this practical model.
Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 
}

### 2018-10-21 tex/intro.tex
Version 3.1

{\color{black}
In order to analyze above-mentioned resources scheduling strategies, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and displays resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to calculate the execution time of each phase of a computing job. 
Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
I/O resource in the map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-heavy tasks.
}

@@

{\color{black}
We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of a computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}

>>>>

{\color{black}
In order to analyze above-mentioned resources scheduling strategies, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-heavy tasks.
}

@@

{\color{black}
We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}

### 2018-10-21 tex/model.tex
Version 3.1

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
the FRQ model quantifies computing and I/O resources and displays them in time dimension. According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on. Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
The current distributed data parallel computing frameworks mostly use \textit{Directed Acyclic Graphs} (DAGs) to describe computation logic. A shuffle phase is required between each adjacent DAG computation phases. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model. After quantifying computing and I/O resources, the FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

@@

We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of shuffle phase. 
The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and \(K \times T_{P\_Shuffle}\) represents the computing overhead. \(K\) is an empirical value. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase need to wait for the transfer results. The overhead is caused by these waiting. The FRQ model uses K to indicate the extent of the waiting.

@@

Figure \ref{fig:model_hadoop} shows one of the optimization methods. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. This scheduling strategy is used by Hadoop MapReduce. After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation. Meanwhile, we found that the I/O resource in the map phase is still idle. This scheduling strategy can be optimized.

@@

In order to verify the above-mentioned two cases when using SCache, we monitor network utilization as Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment. The network utilization remains high until the shuffle phase is completed. This situation is consistent with Figure \ref{fig:model_scache1}. Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment. 
The network utilization has 5 regular peaks. This situation is also consistent with Figure \ref{fig:model_scache2}. Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.

In terms of accuracy, the experimental values are all greater than the calculated values. This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on. In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are within tolerance. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
}

>>>>

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
the FRQ model quantifies computing and I/O resources and visualizes them in time dimension. According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on. Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
The current distributed data parallel computing frameworks mostly use DAGs to describe computation logic. A shuffle phase is required between each adjacent DAG computation phases. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model. After quantifying computing and I/O resources, the FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

@@

We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of shuffle phase. 
The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and \(K \times T_{P\_Shuffle}\) represents the computing overhead. \(K\) is an empirical value. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase needs to wait for the transfer results. The overhead is caused by these waiting. The FRQ model uses K to indicate the extent of the waiting.

@@

Figure \ref{fig:model_hadoop} shows one of the optimization methods. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to Equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see Equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. This scheduling strategy is used by Hadoop MapReduce. After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation. Meanwhile, we found that the I/O resource in the map phase is still idle. This scheduling strategy can be optimized.

@@

In order to verify the above-mentioned two cases when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment. The network utilization remains high until the shuffle phase is completed. This situation is consistent with Figure \ref{fig:model_scache1}. Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment. 
The network utilization has 5 regular peaks. This situation is also consistent with Figure \ref{fig:model_scache2}. Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.

In terms of accuracy, the experimental values are all greater than the calculated values. This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on. In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
}

### 2018-10-21 tex/relatedwork.tex
Version 3.1

However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
Different from these models, our FRQ model quantifies computing and I/O resources and displays them in the time dimension. FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfy our demand.
}

>>>>

However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
}
